\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-11-29 paper.tex
update

A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. When extanding the solution from \cite{wardega2019resilience} in grid-world to continuous configuration spaces, additional reachability analysis is erquired for additional security. Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric extrapolations, such as zonotopes and ellipsoids, to represent a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions. In contrast, our work shifts the focus to reachability analysis during the planning phase, addressing the path optimization problem by incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}. This contribution adds a novel perspective to the existing literature.

This proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.

This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}, the feasibility problem and optimality problem. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. Secondly, security requirements may come at the cost of overall system performance, which is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. In \Cref{sec:cross-trajectory}, these challenges are addressed through introducing additional robots into the MRS. Robots are formed into \emph{sub-teams} and tasked to follow an optimal trajectory without security constraints. The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from the . Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.

@@

\section{Literature review}
\subsection{Reachability analysis}
Reachability analysis is a common step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. A common method is to compute an over-approximation of the reachable space for checking safety properities. Various researches rely on a geometrical extrapolation of the system states like zonotopes and ellipsoids as representation of a compact enclosure of the reachability sets \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive,maiga2015comprehensive}. The work in \cite{}

>>>>

A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. When extanding the solution from \cite{wardega2019resilience} in grid-world to continuous configuration spaces, additional reachability analysis is erquired for additional security. Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric extrapolations, such as zonotopes and ellipsoids, to represent a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.

In contrast, our work shifts the focus to reachability analysis during the planning phase, addressing the path optimization problem by incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}. This contribution adds a novel perspective to the existing literature. This proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.

This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}, the feasibility problem and optimality problem. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. Secondly, security requirements may come at the cost of overall system performance, which is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. In \Cref{sec:cross-trajectory}, these challenges are addressed through introducing additional robots into the MRS. Robots are formed into \emph{sub-teams} and tasked to follow an optimal trajectory without security constraints. The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from one sub-team and join another. Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.

Our algorithm in \Cref{sec:cross-trajectory} focus on the formulation the co-observation planning problem. This algorithm focus on the movement plan for the additional robots (other than the robots needed for objective tasks), their movement are limited follow a pre-defined trajectory with the sub-team, except for situations where they are tasked to perform co-observations with other sub-teams. Only in such case, these robots can deviate from the sub-team and switch the reference trajectory to the corresponding sub-team that requires co-observing, and they will automatically join the sub-team after co-observation. The planning problem can be

@@
